Introducing ICBe: Supplementary Information

### 2022-07-25 replication_paper/arxiv_draft/appendix.Rmd
arxiv draft

---
title: "Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises"

#https://bookdown.org/yihui/bookdown/a-single-document.html
#https://stackoverflow.com/questions/52531637/knitr-rmarkdown-latex-how-to-cross-reference-figures-and-tables-in-2-different/52532269#52532269
#https://stackoverflow.com/questions/51595939/bookdown-cross-reference-figure-in-another-file
#https://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output/51521542#51521542
output: 
  bookdown::pdf_book:
    toc: yes
    latex_engine: xelatex

bibliography: ICBintro.bib

#Disabled several the caused errors
header-includes:
# - \usepackage{xr} \externaldocument{appendix} #External references from the appendix
# - \usepackage{tinytex}
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{natbib} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
#  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
#  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
#  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
#  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
  - \usepackage{subcaption}
  - \usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
  - \usepackage{float}
#  - \usepackage{eso-pic,graphicx,transparent}
#  - \usepackage[perpage]{footmisc}
  - \usepackage{algorithm}
  - \usepackage[algo2e]{algorithm2e}
  - \usepackage{amsmath}
  - \usepackage{afterpage}
  - \usepackage{placeins}
  - \usepackage{rotating, float, caption}
#https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined

---

@@

@@

# Appendix A Corpus and Cases
\hphantom{em}
## Table A1: ICBe Crises and Summary Information {#app:crises}
\hphantom{em}

@@

temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft1.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft2.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft3.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft4.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft5.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft6.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft7.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "figures", "crisis_text_counts_ft8.png"), zoom=1)

\begin{figure}[H]
\caption{ICBe Crises Summary Statistics \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft1.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft2.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft3.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft4.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft5.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft6.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft7.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"../figures/crisis_text_counts_ft8.png"}}
\end{figure}

@@

\begin{figure}[H]
\caption{Graphical User Interface (GUI) for coding ICBe\label{fig:coding_gui}}
\centering{\includegraphics[width=17cm]{../figures/gui_example}}
\end{figure}

@@

\begin{algorithm}[H]
\SetAlgoLined
\KwData{Coder-Sentence-Tokens}
\KwResult{Sentence-Events}
\ForEach{sentence in sentences}{
  \ForEach{concept in concepts}{
    \ForEach{token in tokens}{
      \lIf{expert votes==0}{reject; \tcc*[f]{Require at least one expert vote}}
      \uElseIf{expert votes > expert voters/2}{accept; \tcc*[f]{And a majority of expert votes}}
      \uElseIf{novice votes > novice voters/2}{accept; \tcc*[f]{Or a majority of novice votes}}
    }
    \If{sum(accepted) == 0}{
      sort tags by votes;
      head 1;
      accept; \tcc*[f]{If still no tag, take one with most votes}
    }
  }
  \ForEach{ActorSet in unique(ActorSets)}{
    emit event;
  }
}
\caption{Aggregating Coder-Tokens into Sentence-Events}
\end{algorithm}

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_concept.png'), 
                  plot = p_percent_chose_tag_by_concept, width=8, height=8)
}

\begin{figure}[H]
\caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement}}
\centering{\includegraphics[width=15cm]{../figures/p_percent_chose_tag_by_concept.png}}
\end{figure}

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/figures/p_percent_chose_tag_by_confidence.png'), 
                  plot = p_percent_chose_tag_by_confidence, width=8, height=6)
}

\begin{figure}[H]
\caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement_confidence}}
\centering{\includegraphics[width=15cm]{../figures/p_percent_chose_tag_by_confidence.png}}
\end{figure}

@@

  \ForEach{ edge in edges(g) } {
    \tcc{ Add the edge with the maximum increase in modularity }
    \tcc{ Remove from original graph as a housekeeping trick }
    \lIf{ QPossible[edge]=max(QPossible) }{ append edge to gClustered and remove edge from g; append QPossible to dendrogram }
  }
}
\tcc{ Cut the dendrogram to maximize modularity and return event clusters}
\Return dendrogram where Q(dendrogram)==max(dendrogram) \tcc*[f]{}
\caption{Clustering and counting sentences about the same event}
\end{algorithm}

@@

ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "figures", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"

\begin{figure}[H]
\caption{ Cuban Missile Crisis Synthetic Narrative Recall Matches \label{fig:ft_cuba_recall}}
\centering{\includegraphics[height=21cm]{../figures/ft_cuba_recall.png}}
\end{figure}
\clearpage

@@

ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "figures", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"

\begin{figure}[H]
\caption{ Crimea-Donbas Synthetic Narrative Recall Matches \label{fig:ft_crimea_recall}}
\centering{\includegraphics[height=21cm]{../figures/ft_crimea_recall.png}}
\end{figure}
\clearpage

# Appendix D: Precision

## Figure D1 Crimea-Donbos 
\hphantom{em}

@@

#Loaded above now 
#ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds")) 
fromscratch=F
if(fromscratch){
  temp <- ICBe_events_agreed_markdown %>%
          filter(crisno==471) %>%
          group_by(crisno, sentence_number_int_aligned) %>%
            filter(!duplicated(value_markdown %>% trimws() )) %>% #note there are dupe markdowns for some reason
          ungroup() %>%
          mutate(banding=sentence_number_int_aligned %% 2)
  temp$is_subsstring <- NA
  for(i in 1:nrow(temp)){
    temp$is_subsstring[i] <-   stringr::str_detect(temp$value_markdown %>% tolower() %>% str_replace_all('[^a-z0-9]',"") ,
                                                                                  pattern = fixed(temp$value_markdown[i] %>% tolower() %>% str_replace_all('[^a-z0-9]',"") )
                                                                                ) %>% replace_na(0) %>%  sum()
  }
  temp <-temp %>%
          mutate(value_markdown = ifelse(is_subsstring<=1,value_markdown,'')) %>%
          group_by(sentence_number_int_aligned) %>%
            filter(value_markdown!='' | length(value_markdown)==1) %>%
          ungroup() %>%
          mutate(crisno= ifelse(!is.na(lag(sentence_span_text)) & sentence_span_text==lag(sentence_span_text), "", crisno)) %>%
          mutate(sentence_number_int_aligned= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_number_int_aligned)) %>%
          mutate(sentence_span_text= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_span_text))   #C=crisno, 
        #head(100) %>%

@@

  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "figures", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "figures", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"

@@

\begin{figure}[H]
\caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
\centering{\includegraphics[height=21cm]{../figures/case_study_crimea_precision_part1.png}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[height=21cm]{../figures/case_study_crimea_precision_part2.png}}
\end{figure}
\clearpage

@@

temp <- ICBe_events_agreed_markdown %>% dplyr::select(
  crisno, sentence_span_text,value_markdown,
  act_cooperative , act_deescalate, act_escalate,act_uncooperative,
  interact_decreasecoop,interact_deescalate,
  interact_escalate, interact_increasecoop,
  thinkkind,sayintkind
) %>% pivot_longer(cols=-c(crisno, sentence_span_text,value_markdown)) %>% na.omit() %>% filter(value!='') %>% 
    mutate(value = strsplit(as.character(value), ";")) %>% 
    unnest(value)

temp_sample <- temp %>% mutate(rand=runif(n())) %>% group_by(value)  %>% filter(rand==max(rand)) %>% ungroup() %>% arrange(name, value)

ft_sample_precision_precision1 <- temp_sample %>% 
                                  filter(row_number()<=56) %>%
                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
                                  flextable::as_flextable() %>%
                                  flextable::width( j = 1:2, width=0.5)  %>% 
                                  #flextable::width( j = 2, width=0.25)  %>% 
                                  flextable::width( j = 3, width=0.5)  %>% 
                                  flextable::width( j = 4:5, width=8.0)  %>% 
                                  flextable::fontsize(size = 9, part = "all") %>%
                                  valign(j = 1:3, valign = "top", part = "body") %>%
                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
                                  padding( padding = 1, part = "all") %>% 
                                  bg( i = which( ((1:56) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                  ftExtra::colformat_md(j = 5, part="body")

ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "figures", "ft_sample_precision_precision1.png"), zoom=1) #

ft_sample_precision_precision2 <- temp_sample %>% 
                                  filter(row_number()>=57) %>%
                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
                                  flextable::as_flextable() %>%
                                  flextable::width( j = 1:2, width=0.5)  %>% 
                                  #flextable::width( j = 2, width=0.25)  %>% 
                                  flextable::width( j = 3, width=0.5)  %>% 
                                  flextable::width( j = 4:5, width=8.0)  %>% 
                                  flextable::fontsize(size = 9, part = "all") %>%
                                  valign(j = 1:3, valign = "top", part = "body") %>%
                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
                                  padding( padding = 1, part = "all") %>% 
                                  bg( i = which( ((1:59) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                  ftExtra::colformat_md(j = 5, part="body")

ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "figures", "ft_sample_precision_precision2.png"), zoom=1) #

\hphantom{em}
\begin{figure}[H]
\caption{ Stratified Sentence Examples  \label{fig:ft_sample_precision_precision1}}
\centering{\includegraphics[height=21cm]{"../figures/ft_sample_precision_precision1.png"}}
\end{figure}
\clearpage

\hphantom{em}
\begin{figure}[H]
\centering{\includegraphics[height=21cm]{"../figures/ft_sample_precision_precision2.png"}}
\end{figure}
\clearpage

@@

    print(thiscrisis)
    save_icb_file <- paste0(here::here(), "/replication_paper/figures/p_icb_metro_plot_",thiscrisis,".Rds")

@@

  print(thiscrisis)
  #thiscrisis=471
  plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_mids_file <- paste0(here::here(), "/replication_paper/figures/p_mids_metro_plot_",thiscrisis,".Rds")

@@

## Dyadic ICB
save_file=paste0(here::here(), '/replication_paper/figures/p_icb_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="ICB Dyadic Events"
caption=paste0("Data: Dyadic International Crisis Behavior (ICB) (Hewitt 2003)
             ", p_metro_plot$labels$caption) #tag original to bottom

>>>>

---
title: "Introducing ICBe: Supplementary Information"

csl: pnas.csl
bibliography: paper.bib
biblio-style: unsrt
output: 
  pdf_document:
    toc: true

header-includes:
#  - \usepackage{xr} \externaldocument{appendix} #External references from the appendix
#  - \usepackage{tinytex}
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
#  - \usepackage{natbib} #added for latex citation within huxtable
#  - \usepackage{biblatex} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
#  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
#  - \usepackage{caption}
#  - \usepackage[capposition=top]{floatrow}
#  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
#  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
#  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
#  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
#  - \usepackage{subfigure}
  - \usepackage{subcaption}
  - \usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
  - \usepackage{float}
#  - \usepackage{eso-pic,graphicx,transparent}
#  - \usepackage[perpage]{footmisc}
  - \usepackage{algorithm2e}
  - \usepackage{amsmath}
#  - \usepackage[backend = biber]{biblatex} #added in hopes of getting a bbl
#https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined
---

@@

options(tinytex.clean=F)

@@

```
\clearpage
# Appendix A Corpus and Cases
## Table A1: ICBe Crises and Summary Information {#app:crises}

@@

temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft1.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft2.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft3.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft4.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft5.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft6.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft7.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "arxiv_draft", "crisis_text_counts_ft8.png"), zoom=1)

\begin{figure}[H]
\caption{ICBe Crises Summary Statistics}
\centering{\includegraphics[ height=19cm]{"./crisis_text_counts_ft1.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft2.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft3.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft4.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft5.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft6.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft7.png"}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"./crisis_text_counts_ft8.png"}}
\end{figure}
\clearpage

@@

\begin{figure}[H]
\caption{Graphical User Interface (GUI) for coding ICBe\label{fig:coding_gui}}
\centering{\includegraphics[width=17cm]{./gui_example}}
\end{figure}
\clearpage

@@

\begin{algorithm}[H]
\SetAlgoLined
\KwData{Coder-Sentence-Tokens}
\KwResult{Sentence-Events}
\ForEach{sentence in sentences}{
  \ForEach{concept in concepts}{
    \ForEach{token in tokens}{
      \lIf{expert votes==0}{reject; \tcc*[f]{Require at least one expert vote}}
      \uElseIf{expert votes >= expert voters/2}{accept; \tcc*[f]{And a majority of expert votes}}
      \uElseIf{novice votes >= novice voters/2}{accept; \tcc*[f]{Or a majority of novice votes}}
    }
    \If{sum(accepted) == 0}{
      sort tags by votes;
      head 1;
      accept; \tcc*[f]{If still no tag, take one with most votes}
    }
  }
  \ForEach{ActorSet in unique(ActorSets)}{
    emit event;
  }
}
\caption{Aggregating Coder-Tokens into Sentence-Events}
\end{algorithm}
\clearpage

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_percent_chose_tag_by_concept.png'), 
                  plot = p_percent_chose_tag_by_concept, width=8, height=8)
}

\begin{figure}[H]
\caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement}}
\centering{\includegraphics[width=15cm]{./p_percent_chose_tag_by_concept.png}}
\end{figure}
\clearpage

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/arxiv_draft/p_percent_chose_tag_by_confidence.png'), 
                  plot = p_percent_chose_tag_by_confidence, width=8, height=6)
}

\begin{figure}[H]
\caption{Intercoder Agreement by Concept/Type \label{fig:intercoderagreement_confidence}}
\centering{\includegraphics[width=15cm]{./p_percent_chose_tag_by_confidence.png}}
\end{figure}
\clearpage

@@

  \ForEach{ edge in edges(g) } {
    \tcc{ Add the edge with the maximum increase in modularity }
    \tcc{ Remove from original graph as a housekeeping trick }
    \lIf{ QPossible[edge]=max(QPossible) }{ append edge to gClustered and remove edge from g; append QPossible to dendrogram }
  }
}
\tcc{ Cut the dendrogram to maximize modularity and return event clusters}
\Return dendrogram where Q(dendrogram)==max(dendrogram) \tcc*[f]{}
\caption{Clustering and counting sentences about the same event}
\end{algorithm}
\clearpage

@@

ft_cuba_recall %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_cuba_recall.png"), zoom=1) # webshot = "webshot2"

\begin{figure}[H]
\caption{ Cuban Missile Crisis Synthetic Narrative Recall Matches \label{fig:ft_cuba_recall}}
\centering{\includegraphics[height=21cm]{./ft_cuba_recall.png}}
\end{figure}
\clearpage

@@

ft_crimea_recall %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_crimea_recall.png"), zoom=1) # webshot = "webshot2"

\begin{figure}[H]
\caption{ Crimea-Donbas Synthetic Narrative Recall Matches \label{fig:ft_crimea_recall}}
\centering{\includegraphics[height=21cm]{./ft_crimea_recall.png}}
\end{figure}
\clearpage

# Appendix D: Precision
## Figure D1 Crimea-Donbos 
\hphantom{em}

@@

#Loaded above now 
#ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds")) 
fromscratch=T
if(fromscratch){
  temp <- ICBe_events_agreed_markdown %>%
          filter(crisno==471) %>%
          group_by(crisno, sentence_number_int_aligned) %>%
            filter(!duplicated(value_markdown %>% trimws() )) %>% #note there are dupe markdowns for some reason
          ungroup() %>%
          mutate(banding=sentence_number_int_aligned %% 2)
  temp$is_subsstring <- NA
  for(i in 1:nrow(temp)){
    temp$is_subsstring[i] <-   stringr::str_detect(temp$value_markdown %>% tolower() %>% str_replace_all('[^a-z0-9]',"") ,
                                                                                  pattern = fixed(temp$value_markdown[i] %>% tolower() %>% str_replace_all('[^a-z0-9]',"") )
                                                                                ) %>% replace_na(0) %>%  sum()
  }
  temp <-temp %>%
          mutate(value_markdown = ifelse(is_subsstring<=1,value_markdown,'')) %>%
          group_by(sentence_number_int_aligned) %>%
            filter(value_markdown!='' | length(value_markdown)==1) %>%
          ungroup() %>%
          mutate(crisno= ifelse(!is.na(lag(sentence_span_text)) & sentence_span_text==lag(sentence_span_text), "", crisno)) %>%
          mutate(sentence_number_int_aligned= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_number_int_aligned)) %>%
          mutate(sentence_span_text= ifelse(!is.na(lag(sentence_span_text)) &  sentence_span_text==lag(sentence_span_text), "", sentence_span_text))   #C=crisno, 
        #head(100) %>%

@@

  ft_crimea_precision_part1 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_crimea_precision_part1.png"), zoom=1) # webshot = "webshot2"

@@

  ft_crimea_precision_part2 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "case_study_crimea_precision_part2.png"), zoom=1) # webshot = "webshot2"

@@

\begin{figure}[H]
\caption{ Annexation of Crimea ICB Narrative and ICBe codings \label{fig:case_study_crimea_precision}}
\centering{\includegraphics[height=19cm]{./case_study_crimea_precision_part1.png}}
\end{figure}
\clearpage

\begin{figure}[H]
\centering{\includegraphics[height=21cm]{./case_study_crimea_precision_part2.png}}
\end{figure}
\clearpage

@@

temp <- ICBe_events_agreed %>% left_join(ICBe_events_agreed_markdown) %>% dplyr::select(
  crisno, sentence_span_text,value_markdown,
  act_cooperative , act_deescalate, act_escalate,act_uncooperative,
  interact_decreasecoop,interact_deescalate,
  interact_escalate, interact_increasecoop,
  thinkkind,sayintkind
) %>% pivot_longer(cols=-c(crisno, sentence_span_text,value_markdown)) %>% na.omit() %>% filter(value!='') %>% 
    mutate(value = strsplit(as.character(value), ";")) %>% 
    unnest(value)

set.seed(1) 
temp_sample <- temp %>% mutate(rand=runif(n())) %>% group_by(value)  %>% filter(rand==max(rand)) %>% ungroup() %>% arrange(name, value)

ft_sample_precision_precision1 <- temp_sample %>% 
                                  filter(row_number() %in% 1:22) %>%
                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
                                  flextable::as_flextable() %>%
                                  flextable::width( j = 1:2, width=0.5)  %>% 
                                  #flextable::width( j = 2, width=0.25)  %>% 
                                  flextable::width( j = 3, width=0.5)  %>% 
                                  flextable::width( j = 4:5, width=12.0)  %>% 
                                  flextable::fontsize(size = 9, part = "all") %>%
                                  valign(j = 1:3, valign = "top", part = "body") %>%
                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
                                  padding( padding = 1, part = "all") %>% 
                                  bg( i = which( ((1:22) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                  ftExtra::colformat_md(j = 5, part="body")

ft_sample_precision_precision1 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision1.png"), zoom=1) #

ft_sample_precision_precision2 <- temp_sample %>% 
                                  filter(row_number() %in% 23:54) %>%
                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
                                  flextable::as_flextable() %>%
                                  flextable::width( j = 1:2, width=0.5)  %>% 
                                  #flextable::width( j = 2, width=0.25)  %>% 
                                  flextable::width( j = 3, width=0.5)  %>% 
                                  flextable::width( j = 4:5, width=12.0)  %>% 
                                  flextable::fontsize(size = 9, part = "all") %>%
                                  valign(j = 1:3, valign = "top", part = "body") %>%
                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
                                  padding( padding = 1, part = "all") %>% 
                                  bg( i = which( ((23:54) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                  ftExtra::colformat_md(j = 5, part="body")

ft_sample_precision_precision2 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision2.png"), zoom=1) #

ft_sample_precision_precision3 <- temp_sample %>% 
                                  filter(row_number() %in% 55:90) %>%
                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
                                  flextable::as_flextable() %>%
                                  flextable::width( j = 1:2, width=0.5)  %>% 
                                  #flextable::width( j = 2, width=0.25)  %>% 
                                  flextable::width( j = 3, width=0.5)  %>% 
                                  flextable::width( j = 4:5, width=12.0)  %>% 
                                  flextable::fontsize(size = 9, part = "all") %>%
                                  valign(j = 1:3, valign = "top", part = "body") %>%
                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
                                  padding( padding = 1, part = "all") %>% 
                                  bg( i = which( ((55:90) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                  ftExtra::colformat_md(j = 5, part="body")

ft_sample_precision_precision3 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision3.png"), zoom=1) #

ft_sample_precision_precision4 <- temp_sample %>% 
                                  filter(row_number() %in% 91:115) %>%
                                  dplyr::select(name, value, crisno,  ICB=sentence_span_text, ICBe=value_markdown)  %>%
                                  flextable::as_flextable() %>%
                                  flextable::width( j = 1:2, width=0.5)  %>% 
                                  #flextable::width( j = 2, width=0.25)  %>% 
                                  flextable::width( j = 3, width=0.5)  %>% 
                                  flextable::width( j = 4:5, width=12.0)  %>% 
                                  flextable::fontsize(size = 9, part = "all") %>%
                                  valign(j = 1:3, valign = "top", part = "body") %>%
                                  flextable::line_spacing( space = 1.0, part = "all") %>% 
                                  padding( padding = 1, part = "all") %>% 
                                  bg( i = which( ((91:115) %% 2 )==1 ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                                  ftExtra::colformat_md(j = 5, part="body")

ft_sample_precision_precision4 %>% save_as_image(path=here::here("replication_paper", "arxiv_draft", "ft_sample_precision_precision4.png"), zoom=1) #

\hphantom{em}
\begin{figure}[H]
\caption{ Stratified Sentence Examples  \label{fig:ft_sample_precision_precision1}}
\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision1.png"}}
\end{figure}
\clearpage

\hphantom{em}
\begin{figure}[H]
\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision2.png"}}
\end{figure}
\clearpage

\hphantom{em}
\begin{figure}[H]
\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision3.png"}}
\end{figure}
\clearpage

\hphantom{em}
\begin{figure}[H]
\centering{\includegraphics[height=21cm]{"./ft_sample_precision_precision4.png"}}
\end{figure}
\clearpage

@@

    print(thiscrisis)
    save_icb_file <- paste0(here::here(), "/replication_paper/arxiv_draft/p_icb_metro_plot_",thiscrisis,".Rds")

@@

  print(thiscrisis)
  #thiscrisis=471
  plot_title <- crisno_name_years %>% filter(crisno==thiscrisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_mids_file <- paste0(here::here(), "/replication_paper/arxiv_draft/p_mids_metro_plot_",thiscrisis,".Rds")

@@

## Dyadic ICB
save_file=paste0(here::here(), '/replication_paper/arxiv_draft/p_icb_metro_plot_196.Rds')
p_metro_plot <- readRDS(save_file)
actor_colors <- p_metro_plot$actor_colors
subtitle="ICB Dyadic Events"
caption=paste0("Data: Dyadic International Crisis Behavior (ICB) (Hewitt 2003)
             ", p_metro_plot$labels$caption) #tag original to bottom
